\section{User Manual}

\subsection{Apache Traffic Server}

To run barebones, non-augmented version of ATS, run the following commands:

\begin{enumerate}

\item Clone the FlyingSquid scripts repository

\begin{lstlisting} [language=bash] 
git clone https://github.com/FlyingSquid/scripts.git
\end{lstlisting}

\item Change into the setup directory and execute the setup script.

\begin{lstlisting} [language=bash] 
cd ./scripts/setup
./setup.sh
\end{lstlisting}

This script installs the required dependencies, downloads trafficserver (ATS) into \verb|/mnt|, makes trafficserver, and installs it into \verb|/opt/ts|.

\item

Change into the traffic server directory and start Apache Traffic Server in debug mode (stoppable by \verb|Ctrl-C|):

\begin{lstlisting} [language=bash] 
sudo /opt/ts/bin/traffic_server
\end{lstlisting}

To start or stop trafficserver as a daemon process:
\begin{lstlisting}[language=bash]
sudo /opt/ts/bin/trafficserver stop
sudo /opt/ts/bin/trafficserver start
\end{lstlisting}

\item Make some changes to the ATS proxy configurations file to set it up as a forward proxy:

\begin{lstlisting} [language=bash] 
cd /opt/ts/etc/trafficserver
\end{lstlisting}

Open the \verb|records.config| file and replace the following lines:

\begin{verbatim}
CONFIG proxy.config.reverse_proxy_enabled INT 1
CONFIG proxy.config.url_remap.remap_required INT 1
CONFIG proxy.config.http.cache.http INT 0
\end{verbatim}

With the following lines:

\begin{verbatim}
CONFIG proxy.config.reverse_proxy_enabled INT 0
CONFIG proxy.config.url_remap.remap_required INT 0
CONFIG proxy.config.http.cache.http INT 1
\end{verbatim}

\item Test the proxy with the following command:

\begin{lstlisting} [language=bash] 
curl —-proxy http://127.0.0.1:8080 -o /dev/null http://i.imgur.com/A2FUg9g.png
\end{lstlisting}

\item To view the logging, execute the following command:

\begin{lstlisting} [language=bash] 
/opt/ts/bin/traffic_logcat -f /opt/ts/var/log/trafficserver/squid.blog
\end{lstlisting}

Additionally, ATS can be started with the debug mode to view any logs with a given tag

\begin{lstlisting}[language=bash]
sudo /opt/ts/bin/traffic_server -T<DEBUG_TAG>
\end{lstlisting}


\end{enumerate}

\subsection{ATS with Cloud Caching}

\begin{enumerate}

\item
Download and install the AWS C++ SDK

\begin{lstlisting}[language=bash]
cd /mnt
git clone https://github.com/aws/aws-sdk-cpp.git
mkdir build-aws-sdk-cpp
cd build-aws-sdk-cpp
cmake ../aws-sdk-cpp -DBUILD_ONLY="aws-cpp-sdk-s2" -DCUSTOM_MEMORY_MANAGEMENT=0
make
sudo make install
\end{lstlisting}

\item
Point ATS cache Makefile to the local version of the headers:

Open \verb|/mnt/trafficserver/iocore/cache/Makefile.am| and update line 31 and 32 to reflect where your AWS C++ SDK headers reside. Most likely, they will be updated to the following:

\begin{verbatim}
-I/mnt/aws-sdk-cpp/aws-cpp-sdk-core/include \
-I/mnt/aws-sdk-cpp/aws-cpp-sdk-s3/include
\end{verbatim}

\item
Update the following lines in \verb|/opt/ts/etc/trafficserver/records.config|

\begin{verbatim}
CONFIG proxy.config.http.cache.cloud.enable INT 0
CONFIG proxy.config.http.cache.cloud.provider STRING NULL
\end{verbatim}

To the following to enable cloud caching with AWS:

\begin{verbatim}
CONFIG proxy.config.http.cache.cloud.enable INT 1
CONFIG proxy.config.http.cache.cloud.provider STRING "aws" 
\end{verbatim}

\item
Install the Redis command line interface from: \url{http://redis.io/download}

Set up an initial cluster with the following tutorial:

 \url{http://redis.io/topics/cluster-tutorial}

\item
Recompile ATS and run:

\begin{lstlisting}[language=bash]
cd /mnt/trafficserver
make && sudo make install
sudo /opt/ts/bin/traffic_server
\end{lstlisting}

\end{enumerate}

\subsection{Value-Based Caching Integration}

To run Flying Squid, run the following commands in the following order:

\begin{enumerate}

\item 

\begin{lstlisting} [language=bash] 
sudo /opt/ts/bin/trafficserver start
\end{lstlisting}

ATS will be running on port 8080.

\item 

Set Google chrome or Mozilla Firefox to point to the port on which the TCP Proxy Client (Browser's Interfacing Layer) will run.

\item 

Start up the TCP Proxy Server (ATS's Interfacing Layer) on the machine on which ATS is running:

\begin{lstlisting} [language=bash] 
cd $(RABIN_FINGERPRINT_DIR)/Integration/tcpproxy
make
tcpproxy_server <localhost ip> <tcpproxy_server port> <ATS ip> <ATS port>
\end{lstlisting}

Where \verb|<tcpproxy_server port>| is where \verb|tcpproxy_server| will accept connections.

\item

Start up the TCP Proxy Client (Browser's Interfacing Layer) on the client machine:

\begin{lstlisting} [language=bash] 
cd $(RABIN_FINGERPRINT_DIR)/Integration/tcpclient.
make
tcpproxy_client <localhost ip> <tcpproxy_client port> <tcpproxy_server ip> <tcpproxy_server port>
\end{lstlisting}

Where \verb|<tcpproxy_client port>| is where \verb|tcpproxy_client| will accept connections.

\item

Open the browser that is pointing to the TCP Proxy Client and make request to a website, e.g. http://www.cs.tufts.edu.

\end{enumerate}

\subsection{Rabin Fingerprinting Demo}

\begin{enumerate}

\item 

Start up the Rabin Fingerprinting Server:

\begin{lstlisting} [language=bash] 
cd $(RABIN_FINGERPRINT_DIR)/Server
make
./rabinserver <Rabin Server port> ../Files/HTML/CSWebpage.html ../Files/HTML/CSWebpageWithoutHead.html
\end{lstlisting}

\item Start up the Rabin Fingerprinting Client. Use open for mac and xdj-open for linux in the main.cc file for the Rabin Client.

\begin{lstlisting} [language=bash] 
cd $(RABIN_FINGERPRINT_DIR)/Client
make
./rabinclient localhost <Rabin Server port> test.html
\end{lstlisting}

\item Enter 1 and press enter on the Rabin Fingerprinting Client to receive another file. 

\end{enumerate}

